Including EW and mixed QCD-EW corrections into PDF fits

### 2020-07-28 paper/paper.tex
Sect.3, partial

\acknowledgments
We are grateful to Rikkert Frederix for discussions and explanation about
\textsc{aMCfast}. We acknowledge discussions with 
Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
treatment of EW effects in experimental data. \\
Alessandro Vicini\\
C.S.\ is supported by the European Research Council under the European Unions
Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
MZ thanks the Nikhef institute in Amsterdam,
where he was employed during the early stages of this paper.

>>>>

\acknowledgments
We are grateful to Rikkert Frederix for discussions and explanation about
\textsc{aMCfast}. We acknowledge discussions with 
Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
treatment of EW effects in experimental data. \\
Alessandro Vicini\\
E.R.N. is supported by the European Commission through the Marie
Sk\l odowska-Curie Action ParDHonS FFs.TMDs (grant number 752748).
C.S.\ is supported by the European Research Council under the European Union's
Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
MZ thanks the Nikhef institute in Amsterdam,
where he was employed during the early stages of this paper.

### 2020-07-28 paper/sec-results.tex
Sect.3, partial

We focus on the following three processes: DY lepton-pair production, top-quark
pair production, and Z-boson (lepton-pair) production with non-zero transverse
momentum at the LHC. For each of these processes, we consider the measurments
described below.

\paragraph{DY lepton pair production.}
We select the distribution, single-differential in the invariant mass of the
lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of
mass energy of 7~TeV in the high-mass region
($M_{\ell\bar\ell}>116$~GeV)~\cite{Aad:2013iua}.
We also select the distribution, double-differential in the rapidity and in
the invariant mass of the lepton pair, $y_{\ell\bar\ell}$ and $M_{\ell\bar\ell}$,
measured by the CMS experiment at 7~TeV~\cite{Chatrchyan:2013tia}.
These measurements are currently included as standard in the
NNPDF3.1~\cite{Ball:2017nwa} and MMHT2014~\cite{Harland-Lang:2014zoa} PDF sets,
although with appropriate kinematic cuts that remove the bins at the largest
values of invariant mass, where EW corrections become sizeable.

\paragraph{Top-quark pair production.}
We select the distributions, single-differential in either the transverse
momentum of the top quark, $p_T^t$, or the invariant mass of the top-quark
pair, $m_{t\bar t}$, measured by the ATLAS and CMS experiments at a centre-of-mass
energy of 8~TeV~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
been extensively studied in the context of PDF fits in
Refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}.
Because EW corrections are significantly smaller for distributions differential
in the rapidity of either the top quark or the top-quark
pair~\cite{Czakon:2017wor}, these were preferred for inclusion in the NNPDF3.1
set~\cite{Ball:2017nwa}.

\paragraph{$Z$-boson production with non-zero transverse momentum.}
We select the distribution, single-differential in the transverse momentum of
the $Z$ boson, $p_T^Z$, measured by the CMS experiment at a centre-of-mass
energy of 13~TeV~\cite{Sirunyan:2019bzr}. This measurement has not been
included in a PDF determination yet. Given that it has sub-percent
uncertainties, it is expected that EW corrections will be essential to
achieve a good description of it, and to constrain accurately the PDFs.
A similar challenge was observed in similar measurements, from the
ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa} experiment at a
centre-of-mass energy of 8~TeV, in Ref.~\cite{Boughezal:2017nla}, which lead to
their partial inclusion (upon the selection of an appropriate kinematic cut)
in the NNDPF3.1 PDF set~\cite{Ball:2017nwa} and in variants of the CT18 PDF
set~\cite{Hou:2019efy}.

@@

We discuss,
\begin{itemize}
\item in section~\ref{sec:atlas-high-mass-dy}, ATLAS high-mass DY lepton-pair production at \SI{7}{\tera\electronvolt} \cite{Aad:2013iua}, measuring $\mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ for the lepton-pair invariant mass $M_{\ell \bar{\ell}} > \SI{116}{\giga\electronvolt}$,
\item in section~\ref{sec:cms-dy}, CMS DY lepton-pair production at \SI{7}{\tera\electronvolt} \cite{Chatrchyan:2013tia}, measuring $\mathrm{d} \sigma / \mathrm{d} y_{\ell \bar{\ell}}$ for six slices in the range $\SI{20}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt}$,
\item in section~\ref{sec:atlas-top-pair-production}, ATLAS top-pair production at \SI{8}{\tera\electronvolt} \cite{Aad:2015mbv}, measuring
\begin{itemize}
\item the transverse momentum of the reconstructed top, $\mathrm{d} \sigma / \mathrm{d} p_\mathrm{T}^\mathrm{t}$,
\item its rapidity, $\mathrm{d} \sigma / \mathrm{d} y_\mathrm{t}$,
\item the invariant mass of the reconstructed top pair, $\mathrm{d} \sigma / \mathrm{d} M_{\mathrm{t} \bar{\mathrm{t}}}$, and
\item its rapidity, $\mathrm{d} \sigma / \mathrm{d} M_{\mathrm{t} \bar{\mathrm{t}}}$,
\end{itemize}
\item in section~\ref{sec:cms-transverse-momentum}, CMS transverse momentum of the Z boson at \SI{13}{\tera\electronvolt} \cite{Sirunyan:2019bzr}, measuring $\mathrm{d} \sigma / \mathrm{d} p_\mathrm{Z}$ for $p_\mathrm{Z} > \SI{20}{\giga\electronvolt}$.
\end{itemize}
We used the MC \texttt{mg5\_aMC@NLO}~\cite{} and the PDF set \texttt{NNPDF31\_as\_0118\_luxqed}~\cite{} to generate the predictions.
The chosen PDF set contains a photon PDF calculated from the LUXQED method~\cite{}.
For each process---except top-pair production, which has stable tops in the final state---we use a complex-mass scheme~\cite{} as described in ref.~\cite{}.
The values of the most important parameters are
\begin{equation}
\begin{aligned}
M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
M_\mathrm{Z} &= \SI{90}{\giga\electronvolt} \text{,} \quad &
m_\mathrm{t} &= \SI{170}{\giga\electronvolt} \text{,} \\
\Gamma_\mathrm{W} &= \SI{2}{\giga\electronvolt} \text{,} &
\Gamma_\mathrm{Z} &= \SI{2}{\giga\electronvolt} \text{,} &
G_\mu &= \text{.}
\end{aligned}
\end{equation}

\subsection{ATLAS high-mass DY lepton-pair production at \SI{7}{\tera\electronvolt}}
\label{sec:atlas-high-mass-dy}

\begin{equation}
\begin{gathered}
p_\mathrm{T}^\ell > \SI{25}{\giga\electronvolt} \text{,} \quad |\eta_\ell| < 2.5 \text{,} \\
\SI{116}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt} \text{,}
\end{gathered}
\end{equation}

\subsection{CMS DY lepton-pair production at \SI{7}{\tera\electronvolt}}
\label{sec:cms-dy}

\begin{equation}
\begin{gathered}
p_\mathrm{T}^{\ell_1} > \SI{14}{\giga\electronvolt} \text{,} \quad p_\mathrm{T}^{\ell_2} > \SI{9}{\giga\electronvolt} \text{,} \quad |\eta_\ell| < 2.4 \text{,} \\
|\eta_{\ell \bar{\ell}}| < 2.4 \text{,} \quad \SI{20}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt} \text{,}
\end{gathered}
\end{equation}

\subsection{ATLAS top-pair production at \SI{8}{\tera\electronvolt}}
\label{sec:atlas-top-pair-production}

\subsection{CMS transverse momentum of the Z boson at \SI{13}{\tera\electronvolt}}
\label{sec:cms-transverse-momentum}

\begin{equation}
\begin{gathered}
p_\mathrm{T}^\ell > \SI{25}{\giga\electronvolt} \text{,} \quad |\eta_\ell| < 2.4 \text{,} \quad M_\mathrm{Z} - \SI{15}{\giga\electronvolt} < M_{\ell \bar{\ell}} < M_\mathrm{Z} + \SI{20}{\giga\electronvolt} \text{,} \\
|\eta_{\ell \bar{\ell}}| < 2.4 \text{,} \quad \SI{20}{\giga\electronvolt} < p_\mathrm{T}^{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt} \text{,}
\end{gathered}
\end{equation}

>>>>

We focus on the following three processes: DY lepton-pair production, top-quark
pair production, and Z-boson (lepton-pair) production with non-zero transverse
momentum at the LHC. For each of these processes, we consider the measurements
described below.

\paragraph{DY lepton pair production.}
We select the distribution, single-differential in the invariant mass of the
lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of
mass energy of 7~TeV in the high-mass region
($M_{\ell\bar\ell}>116$~GeV)~\cite{Aad:2013iua}.
We also select the distribution, double-differential in the rapidity and in
the invariant mass of the lepton pair, $y_{\ell\bar\ell}$ and $M_{\ell\bar\ell}$,
measured by the CMS experiment at a centre-of-mass energy of
7~TeV~\cite{Chatrchyan:2013tia}.
These measurements are currently included as standard in the
NNPDF3.1~\cite{Ball:2017nwa} and MMHT2014~\cite{Harland-Lang:2014zoa} PDF sets,
although with appropriate kinematic cuts that remove the bins at the largest
values of invariant mass, where EW corrections become sizeable.

\paragraph{Top-quark pair production.}
We select the distributions, single-differential in either the transverse
momentum of the top quark, $p_T^t$, or the invariant mass of the top-quark
pair, $m_{t\bar t}$, measured by the ATLAS and CMS experiments at a centre-of-mass
energy of 8~TeV~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
been extensively studied in the context of PDF fits in
Refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}, and
included by default in the CT18~\cite{Hou:2019efy} analysis.
Because EW corrections are significantly smaller for distributions differential
in the rapidity of either the top quark or the top-quark
pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
in the NNPDF3.1 analysis~\cite{Ball:2017nwa}.

\paragraph{$Z$-boson production with non-zero transverse momentum.}
We select the distribution, single-differential in the transverse momentum of
the $Z$ boson, $p_T^Z$, measured by the CMS experiment at a centre-of-mass
energy of 13~TeV~\cite{Sirunyan:2019bzr}. So far, this measurement has not been
included in any PDF determination. Because it has sub-percent uncertainties,
EW corrections are expected to be essential in order to achieve a good
description of it, and to constrain accurately the PDFs. Analogous measurements,
from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
experiments at a centre-of-mass energy of 8~TeV were partly included (upon the
selection of an appropriate kinematic cut that excluded bins with large EW
corrections) in the NNDPF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
the CT18 PDF set~\cite{Hou:2019efy}.

@@

We generate each process by means of the Universal FeynRules Output
(UFO)~\cite{Degrande:2011ua} model {\tt loop\_qcd\_qed\_sm\_Gmu},
included as standard in {\sc MG5\_aMC}. It contains the UV and $R_2$
counterterms relevant to NLO QCD and EW corrections, the latter in the
$\overline{G}_\mu$ scheme. The model features five massless quark flavours,
sets the CKM matrix equal to the identity, and is compatible with the usage of
the complex mass (CM) scheme for all massive particles, see
Ref.~\cite{Frederix:2018nkq} for details. We use this scheme
for all processes that do not involve stable top quarks in the final state.
The photon is always considered as part of the proton in the initial state and
of any hadronic jet produced in the final state: PI effects and EW corrections
are therefore treated on the same footing. We use a PDF set that contains a
consistently defined photon PDF, namely
{\tt NNPDF31\_as\_0118\_luxqed}~\cite{Bertone:2017bme}. We evaluate the PDF
uncertainty associated to the theoretical predictions a posteriori, that is,
we convolve the fast interpolation grid generated with {\sc PineAPPL} with
each member in the PDF set, and we compute the associated standard deviation.

The central values of the renormalisation and factorisation scales, $\mu_R$ and
$\mu_F$, are chosen, for each process, as follows. In the case of DY lepton pair
production, we use the fixed scale $\mu_R=\mu_F=M_Z$, where $M_Z$ is the mass
of the $Z$-boson, for the ATLAS measurement, and the dynamic scale
$\mu_R=\mu_F=$ for the CMS measurement.
In the case of top-quark pair production, we use the dynamic scales
$\mu_R=\mu_F=\sqrt{m_t^2+(p_T^t)^2}{\Big /}2$ for the distribution differential
in the transverse momentum of the top quark, and $\mu_R=\mu_F=H_T/4$ for the
distribution differential in the invariant mass of the top-quark pair, where
$H_T=\sqrt{m_t^2+(p_T^t)^2}+\sqrt{m_t^2+(p_T^{\bar{t}})}$, with $m_t$,
$p_T^t$ and $p_T^{\bar t}$ the mass of the top quark and the transverse momenta
of the top and antitop quarks, respectively. These choices were demonstrated
to maximise the convergence of the perturbative expansion~\cite{Czakon:2016dgf}.
In the case of $Z$-boson production with non-zero transverse momentum, we use
$\mu_R=\mu_F=M_Z$. In order to estimate the missing higher-order uncertainty,
we allow the events to be reweighted in the Monte Carlo generation upon scale
variations. As is customary, the factorisation and renormalisation scales
are varied down to a factor $1/2$ and up to a factor $2$.

The values of the relevant physical parameters are chosen as
\begin{equation}
%\begin{aligned}
M_\mathrm{W} = \SI{80}{\giga\electronvolt} \text{,} \quad 
M_\mathrm{Z} = \SI{90}{\giga\electronvolt} \text{,} \quad 
m_\mathrm{t} = \SI{170}{\giga\electronvolt} \text{,} \quad
\Gamma_\mathrm{W} = \SI{2}{\giga\electronvolt} \text{,} \quad
\Gamma_\mathrm{Z} = \SI{2}{\giga\electronvolt} \text{,} 
\label{eq:parameters}
%\end{aligned}
\end{equation}
where $M_W$, $M_Z$ and $m_t$ are the values of the $W$-boson, $Z$-boson and
top quark masses, respectively, and $\Gamma_W$ and $\Gamma_Z$ are the width of
the $W$-boson and of the $Z$-boson, respectively. The value of the strong
coupling is chosen consistently with the PDF set, $\alpha_s(M_Z)=0.118$.

Finally, we implement the kinematic cuts specified in the corresponding
experimental analyses. In the case of high-mass DY lepton pair
production at 7~TeV measured by ATLAS, we require $p_T^\ell>25$~GeV,
$|\eta_\ell|<2.5$ and 116~GeV$<M_{\ell\bar\ell}<$ 1500~GeV for the transverse
momentum and the rapidity of each lepton and for the invariant mass of the
lepton pair, respectively. In the case of the DY lepton-pair production at
7~TeV measured by CMS, we require $p_T^{\ell_1}>14$~GeV, $p_T^{\ell_2}>9$~GeV,
$|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and 20~GeV$<M_{\ell\bar\ell}<$ 1500~GeV
for the transverse momentum and the rapidity of each lepton, and for the
rapidity and the invariant mass of the lepton pair. In the case of $Z$-boson
production with non-zero transverse momentum at 13~TeV measured by CMS, we
require $p_T^\ell>25$~GeV, $|\eta_\ell|<2.4$,
$M_Z$-15~GeV$<M_{\ell\bar\ell}<M_Z$+20~GeV,
$|\eta_{\ell\bar\ell}|<2.4$ and 20~GeV$<p_T^{\ell\bar\ell}<1500$~GeV for the
transverse momentum and rapidity of each lepton, and for the invariant mass,
rapidity and transverse momentum of the lepton pair.

\subsection{Numerical results}
\label{subsec:numerical_results}
